---
title: "Getting started with binomial"
author: "Angie Chen"
date: "r Sys.Date() "
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(cointoss)
```

## Overview

"binomial" is an R package that provides functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

## Mathematical functions

The binomial package includes functions to help you calculate measures such as mean, variance, mode, skewness, and kurtosis. For example, you can use bin_mean to find the mean:

```{r}
bin_mean(34, 0.4)
```

## Calculating probability of success

The package also contains functions to help you measure success rates. bin_choose calculates number of compliations in which k successes can occur in n trials, while bin_probability calculates probability of success in a number of trials. 

```{r}
bin_choose(5, 0)
bin_probability(success = 55, trials = 100, prob = 0.45)
```

## Creating a binomial probability distribution

You can display your findings in a data frame. This creates a visualization of the probability of each number of successes occuring. 

```{r}
bin_distribution(trials = 5, prob = 0.5)
```

You can also create a cumulative version that adds up the probabilities as the success rate increases.

```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

## Creating a plot

The next step is to use your data frame to visualize your data in a graph. 

```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

## Summarizing your findings

Finally, you can summarize your findings using the summary function.

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

